### 2016-10-25 sec-results.tex
Fix spacing issue with use of macro for MOOC names.

\section{Results}
To qualitatively evaluate our model, we look at the latent state
representations we learn by fitting the model to the log data associated
with two different Coursera MOOCs: \textretrieval and \sustain.

>>>>

\section{Results}
To qualitatively evaluate our model, we can look at the latent state
representations we learn by fitting the model to some MOOC log data. We can
also inspect the transition matrix between the latent states discovered by
the model.

Specifically, we look at the MOOC logs associated with two different
Coursera MOOCs offered by \UIUC{}: \textretrieval{} and \sustain{}.  The
\textretrieval{} MOOC represents a highly technical computer science course,
where the \sustain{} MOOC is more representative of a humanities course. We
picked these two MOOCs because of their vastly different content domains.
